---
title: "HW7 Instructions"
author: "Data Science 2"
editor: visual
format:
  html:
    embed-resources: true
execute:
  echo: true
  message: false
  warning: false
---

```         
```

```{r setup}
library(tidyverse)
library(tidytext)
library(schrute)
library(kableExtra)
library(topicmodels)
```

```{r, warning=FALSE, message=FALSE}
office <- theoffice
```

# The Office

Let's continue to work with *The Office* text from the [schrute](https://cran.r-project.org/web/packages/schrute/index.html) package.

# Primary Topics

For each season (not each episode anymore), determine the primary topics for the show using 1) a TF-IDF approach and 2) an LDA approach. You should do at least some cleaning of the data to exclude words that don't make sense.

#### Data Cleaning:

```{r, warning=FALSE, message=FALSE}
office2 <- office |> 
  group_by(season) |> 
  summarize(text = paste(text, collapse = " "))

# Custom stopwords
extra_stopwords <- c("yeah", "hey", "uh", "gonna", "um")

office3 <- office2 |> 
  unnest_tokens(word, text) |> 
  anti_join(stop_words) |> 
  #extra words identified after LDA/TF-IDF
  filter(!word %in% extra_stopwords) |> 
  #entirely letters
  filter(str_detect(word, "^[a-z]+$")) |> 
  #no sound effects
  filter(!str_detect(word, "(.)\\1{2,}"))


```

#### TF-IDF

```{r, warning=FALSE, message=FALSE}
#Create Term Freq
office_tf <- office3 |> 
  count(season, word) |> 
  group_by(season) |> 
  mutate(TF = n / sum(n)) |> 
  ungroup()

#Doc Freq
office_tf |> 
  distinct(season, word) |> 
  count(word, sort = TRUE) |> 
  rename(DT = n) |> 
  head(10)

#Doc Freq Prop and ITF
office_idf <- office_tf |> 
  distinct(season, word) |> 
  count(word) |> 
  rename(DT = n) |> 
  mutate(DF = DT / {office3 |> distinct(season) |> nrow()},
         IDF = 1 / DF,
         logIDF = log(IDF))

#TF-IDF
office_tf_idf <- office_tf |> 
  left_join(office_idf, by = "word") |> 
  mutate(TFIDF = TF * logIDF)

#Primary Words by Season
office_tf_idf |> 
  group_by(season) |>             # group by season
  slice_max(TFIDF, n = 10) |>     # get top 10 words per season
  select(season, word, TFIDF) |>  # keep only the columns you care about
  ungroup()
```

```{r, warning=FALSE, message=FALSE}
#Top Word Each Season
#Primary Words by Season
office_tf_idf |> 
  group_by(season) |>             # group by season
  slice_max(TFIDF, n = 1) |>     # get top 10 words per season
  select(season, word, TFIDF) |>  # keep only the columns you care about
  ungroup()
```

This is pretty interesting. I've watched the show through a few times, and these one word TF-IDF top results do a really good job of capturing the major theme. Season 3 and 5 would require a second look. I know in season3, they sing "In the Jungle" which has severage usages of the word, thus likely skewing the result, given its uniqueness.

#### LDA

```{r, warning=FALSE, message=FALSE}
#DTM
office_dtm <- office3 |> 
  count(season, word) |> 
  cast_dtm(document = season, term = word, value = n)

#fit model
office_lda <- LDA(office_dtm, k = 3)

#top words
office_topics <- tidy(office_lda, matrix = "beta") |> 
  mutate(topic = paste0("topic", topic)) |> 
  group_by(topic) |> 
  slice_max(beta, n = 10) |> 
  ungroup()

#table
office_topics |> 
  select(topic, term, beta) |> 
  head()
```

```{r, warning=FALSE, message=FALSE}
office_topics |> 
  ggplot(aes(beta, term |> reorder(beta), fill = topic |> as.factor())) +
  geom_col(show.legend = F) +
  facet_wrap(~topic, scales = "free") +
  scale_y_reordered()
```

I made a subjective decision to not remove the proper nouns. I figured some seasons may have a central theme around a character, like the season Michael left. However, it seems the LDA approach was primarily impacted by the characters. TF-IDF gave extra emphasis to unique words across the seasons, and many proper nouns were common across the seasons. This is not true for LDA.
